---
title: Deeper into deployment
subtitle: Deploy and maintain models with vetiver (R)
format: html
---

## Create your vetiver model 🏺

```{r}
library(tidyverse)
library(tidymodels)
library(arrow)
set.seed(123)

path <- here::here("data", "housing.parquet")
housing <- read_parquet(path)

set.seed(123)
housing_split <- housing |>
  mutate(price = log10(price)) |>
  initial_split(prop = 0.8)
housing_train <- training(housing_split)
housing_test <- testing(housing_split)

housing_fit <-
  workflow(
    price ~ bedrooms + bathrooms + sqft_living + yr_built,
    rand_forest(trees = 200, mode = "regression")
    ) |>
  fit(data = housing_train)

v <- vetiver_model(___, ___)
v
```

## Docker 🐳

See `docker-rstats.qmd` in this same folder if you want to work along with the Docker demo.

## Model metrics as metadata 🎯

Compute metrics for your model:

```{r}
housing_metrics <-
    augment(housing_fit, new_data = ___) |>
    metrics(truth = price, estimate = .pred)

housing_metrics
```

Store these metrics as vetiver metadata:

```{r}
library(vetiver)
v <- vetiver_model(
  ___, 
  ___, 
  metadata = list(metrics = ___)
)
```

Write a new version of your pin:

```{r}
library(pins)
board <- ___
board |> ___
```

Get your metrics metadata:

```{r}
extracted_metrics <- 
  board |> 
  pin_meta(___) |> 
  pluck("user", "metrics") |> 
  as_tibble()

extracted_metrics
```

If you have time, redeploy your model and then get **your neighbor's** metrics metadata by calling the `/metadata` endpoint of their model:

```{r}
url <- ___
r <- httr::content(httr::GET(url), as = "text", encoding = "UTF-8")
jsonlite::fromJSON(___) |> 
  pluck("user", "metrics") |> 
  as_tibble()
```

## Add a new endpoint to your API ✨

Write a `plumber.R` file:

```{r}
vetiver_write_plumber(board, ___)
```

Open the file and run it locally; use the "Run API" button in RStudio.

Add a new endpoint to this file! 

One option is to read in a model explainer, make a new handler function, and add `library(DALEXtra)` and `library(dplyr)`:

```r
board <- board_url(c(
  shap_explainer = "https://pub.demo.posit.team/public/seattle-shap-rstats/"
))
explainer <- pin_read(board, "shap_explainer")

handler_explain <- function(req) {
    new_data <- req$body
    new_data <- vetiver_type_convert(new_data, v$prototype)
    shap <- predict_parts(explainer, new_data, type = "shap", B = 25)
    shap |> group_by(variable) |> summarise(contribution = mean(contribution))
}
```

Change your `#* @plumber` decorated function so its body looks like:

```r
pr |>  
  vetiver_api(v) |> 
  pr_post(path = "/explain", handler = handler_explain)
```

After you add a new endpoint, run the API locally again.
