---
title: Monitor your model
subtitle: Deploy and maintain models with vetiver (R)
format: html
---

## Data for modeling & data for monitoring 🤝

```{r}
library(arrow)

path1 <- here::here("data", "housing.parquet")
housing <- read_parquet(path1)

path2 <- here::here("data", "housing_monitoring.parquet")
housing_new <- read_parquet(path2)
```

Compare the modeling and monitoring datasets:

```{r}
## make a plot or table
```

## Monitor metrics over time ⏳

```{r}
library(vetiver)
library(tidymodels)
url <- "https://pub.demo.posit.team/public/seattle-housing-rstats/predict"
endpoint <- vetiver_endpoint(url)

metrics_df <-
  augment(endpoint, new_data = housing_new) |>
    mutate(price = log10(price)) |>
    vetiver_compute_metrics(
      date,
      ___, 
      price,
      .pred,
      metric_set = metric_set(rmse, rsq, mae)
  )

metrics_df
```

```{r}
vetiver_plot_metrics(metrics_df)
```

Read about how you can use pins for versioning metrics: <https://rstudio.github.io/vetiver-r/reference/vetiver_pin_metrics.html>

## ML metrics ➡️ organizational outcomes

What is the mean absolute percentage error?

```{r}
augment(endpoint, housing_new) |> 
  mutate(.pred = 10 ^ .pred) |> 
  group_by(___) |> 
  ___(price, .pred)
```

```{r}
## make a visualization
```

## Create a monitoring dashboard or report 📊

To wrap up, create a model monitoring dashboard or report and publish it to Connect. You have a few options:

- Open the `04-monitor-dashboard.Rmd`, make any changes you like (for example, different metrics or visualizations), knit it, and publish to Connect.
- Open a fresh copy of the dashboard template in RStudio by choosing "File" ➡️ "New File" ➡️ "R Markdown" ➡️ "From Template" ➡️ "Vetiver Dashboard". Update this template for _your_ model and publish to Connect.
